XX

### 2019-05-25 paper/manuscript.Rmd
Some basic methods

>>>>

```{r}
loadd(config)
loadd(int_metadata)
n_published_studies <- int_metadata$reference %>%
  unique() %>%
  stringr::str_detect(pattern = "unpubl", negate = TRUE) %>%
  sum()
```

We downloaded plant pollinator networks from the Web of Life up to `r format(as.Date(config$raw_data_retrieved), "%b %d, %Y")`. 
This included pollination networks from `r n_published_studies` studies which included plant-pollinator interactions in `r dplyr::n_distinct(int_metadata$loc_id)` independent locations (Figure X).
